### 2022-01-17 src-latex/parts/40-ner-approaches.tex
One sentence per line

% !TeX root = ../main-paper.tex
\section{NER Approaches}
Four approaches, one rules-based, three learning-based.

@@

\subsubsection{Spacy 3 NER pipeline}
The \textit{of the shelf} NLP library SpaCY offers a named entity recognition tool based on an ad hoc architecture which has not been yet published but is explained by the developers on their website. Although the latest version of SpaCy (v3) leverages BERT models, we could not use them as no NER pipeline is available for the French language at the time of our experiments\footnote{https://spacy.io/models/fr}. The vanilla NER pipeline is two-fold. Words are first encoded into local context-aware embeddings using a window-based CNN similar to~\cite{collobert2011}. The decision layer is an adaptation of the transition-based model presented in~\cite{lample2016}. As words are processed sequentially, their vectors are concatenated with those in the last known entities to encode the nearby predicted semantics as a dynamic attention mechanism. The classification layer relies on a finite-state machine whose transition probabilities are learned using a multi-layer perceptron.
In 2018~\cite{won2018} compared SpaCy's vanilla NER performances on historical texts about places with several other software packages (Stanford-NER, Ner-Tagger, Edinburgh Geopoarser and Polyglot). Results showed SpaCy to be average with a F1-score of 0.57. The SpaCy developers claims an accuracy of 0.85 for the English NER pipeline \textit{en\_core\_web\_lg} on the OntoNotes 5.0 corpus\footnote{https://spacy.io/usage/facts-figures}.

@@

\begin{itemize}
    \item regexp
    \item CamemBERT finetuned with wikiner-fr + gold dataset (clean texts)
    \item CamemBERT finetuned with wikiner-fr + gold dataset (clean texts + pretrained on raw texts (Pero ? Kraken ? Both ?)
\end{itemize}

% Other possibilities:
1. Traditional ML based:
    Conditional Random Fields (CRF) - https://pypi.org/project/sklearn-crfsuite/
    Maximum-entropy Markov model

2. Neural Networks based:
    LSTMs, bi-LSTM - https://github.com/flairNLP/flair
    CNNs (SpaCy uses CNN based architecture)
    Transformers (Spacy has recently launched it) - https://spacy.io/universe/project/spacy-transformers

>>>>

% !TeX root = ../main-paper.tex
\section{NER Approaches}

Previous work on the influence of OCR errors on NER models shows that it is preferable to reuse a model trained on modern data and adapt it to OCRised historical texts using supervised or unsupervised approaches. This is why, in our tests, we have selected two deep learning-based NER approaches trained on French texts: Spacy 3 NER pipeline and CamemBERT.

@@

\subsubsection{Spacy 3 NER pipeline}
The \textit{of the shelf} NLP library SpaCY offers a named entity recognition tool based on an ad hoc architecture which has not been yet published but is explained by the developers on their website. Although the latest version of SpaCy (v3) leverages BERT models, we could not use them as no NER pipeline is available for the French language at the time of our experiments\footnote{https://spacy.io/models/fr}.
The vanilla NER pipeline is two-fold. Words are first encoded into local context-aware embeddings using a window-based CNN similar to~\cite{collobert2011}.
The decision layer is an adaptation of the transition-based model presented in~\cite{lample2016}.
As words are processed sequentially, their vectors are concatenated with those of the last known entities to encode the nearby predicted semantics as a dynamic attention mechanism.
The classification layer relies on a finite-state machine whose transition probabilities are learned using a multilayer perceptron.
In 2018~\cite{won2018} compared SpaCy's vanilla NER performance on historical texts about places with several other software packages (Stanford-NER, Ner-Tagger, Edinburgh Geopoarser and Polyglot). Results showed SpaCy to be average with a F1-score of 0.57.
The SpaCy developers claimed an accuracy of 0.85 for the English NER pipeline \textit{en\_core\_web\_lg} on the OntoNotes 5.0 corpus\footnote{https://spacy.io/usage/facts-figures}.

@@

Language model embeddings pretrained using Transformers, like BERT, have become a new paradigm for NER\cite{li2020}. Indeed, these embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec and they can be further fine-tuned for NER task by adding an additional output layer. Moreover, they can also be further pretrained in an unsupervised way on historical texts for domain adaptation.

As our directories are written in French, we chose the language model CamemBERT \cite{martin-etal-2020-camembert}, a Transformer model trained on a French corpus. We started from the CamemBERT-ner model already fine-tuned on WikiNER-fr corpus and published on the Hugging Face repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}}. Its output layer is a linear model with a Softmax function.

For our experiments, two models are derived. One is produced by fine-tuning this generic model on our ground truth dataset.
The second is created by adapting the embeddings of this model using raw directory texts, randomly selected and extracted with PERO OCR. The base model is pretrained on these texts for two tasks, namely, Next Sentence Prediction (NSP) and Masked Language Model (MLM). Finally, the resulting model is also fine-tuned using our ground truth corpus.

% Other possibilities:
%1. Traditional ML based:
%    Conditional Random Fields (CRF) - https://pypi.org/project/sklearn-crfsuite/
%    Maximum-entropy Markov model

%2. Neural Networks based:
%    LSTMs, bi-LSTM - https://github.com/flairNLP/flair
%    CNNs (SpaCy uses CNN based architecture)
%    Transformers (Spacy has recently launched it) - %https://spacy.io/universe/project/spacy-transformers
